|

### 2020-07-08 paper.Rmd
Added link to PLOS One example.
Deleted header.tex because of errors.

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown*^[*Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Paul C. Bauer
  | Mannheim Centre for European Social Research
date: |
  |       
  |
  | `r gsub("^0", "", format(Sys.time(), "%d %B, %Y"))`
  |
  | Feedback? 
  | mail@paulcbauer.eu
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    includes:
      in_header: header.tex
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 5 input files I created --- `paper.rmd`, `header.tex`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). Ignore the other files.

@@

* ...a `paper.rmd` file (the underlying R Markdown file).
* ...a `header.tex` file (a tex file for document structure).
* ...a `references.bib` file (the bibliography).
    + I use paperpile to manage my references and export the `.bib` file into the folder that contains my `.rmd` file.
* ...a `data.csv` file (some raw data).
* ... a `american-sociological-association.csl` file that defines the style of your bibliography.^[You can download various citation style files from this webpage: https://github.com/citation-style-language/styles.]

@@

```{r tab3, echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(knitr)
library(kableExtra)
kable(cars[1:10,], row.names = TRUE, 
      caption = 'Table with kable() and kablestyling()', 
      format = "latex", booktabs = T) %>%
        kable_styling(full_width = T, 
                      latex_options = c("striped", 
                                        "scale_down",
                                        "HOLD_position"),
                      font_size = 10)
```

@@

# Additional tricks for publishing
* Make your script anonymous
    + Simply put a `<!-- ... -->` around any identifying information, e.g., author names, title footnote etc.
* Counting words
    + Use adobe acrobat (commerical software) to convert your file to a word file. Then open in word and delete all the parts that shouldn't go into the word count. The word count is displayed in the lower right.
    + Use an one of the online services to count your words (search for "pdf word count")
* Appendix: You can change the numbering format for the appendix in the rmd file
    + What is still not possible in this document is to automatically have separate reference sections for paper and appendix.

>>>>

---
title: |
  |
  | 
  | \vspace{1cm}Writing a reproducible paper
  | in R Markdown*^[*Corresponding address: mail@paulcbauer.eu. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.]\vspace{0.5cm}
  |
author: |
  | Paul C. Bauer
  | Mannheim Centre for European Social Research
date: |
  |       
  | First version: December 14, 2018
  | This version: `r gsub("^0", "", format(Sys.time(), "%B %d, %Y"))`
  |
  | Feedback? 
  | mail@paulcbauer.eu
  |
linestretch: 1.2
colorlinks: true
abstract: \noindent\setstretch{1}The present paper provides a template for a reproducible scientific paper written in R Markdown. Below I outline some of the "tricks"/code (e.g., referencing tables, sections etc.) I had to figure out to produce this document. The underlying files which produce this document can be downloaded [here](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). I think I got pretty far but there is always room for improvement and more automatization, in parallel to the incredible developments in R and Rstudio (bookdown etc.). I intend to update this file when I discover more convenient code (you can follow any updates through the corresponding [github repo](https://github.com/paulcbauer/Writing_a_reproducable_paper_in_rmarkdown/)).\vspace{.8cm}
bibliography: references.bib
csl: american-sociological-association.csl
output:
  bookdown::pdf_document2:
    toc: no
    keep_tex: true
mainfont: Times New Roman
sansfont: Times New Roman
fontsize: 12pt
link-citations: true
documentclass: article
geometry: margin=1in
always_allow_html: yes
---

@@

* ...install [R](https://www.r-project.org/) and [Rstudio](https://www.rstudio.com/) (most recent versions) [@R2017; @Rstudio2015].
* ...install [tinytex](https://yihui.name/tinytex/), a lightweight version of Tex Live [@markdown2017; @tinytex].
```{r eval=FALSE, include=TRUE}
install.packages(c('tinytex', 'rmarkdown'))
tinytex::install_tinytex()
```
* ...install the packages below using the code below [@bookdown1; @bookdown2; @knitr1; @knitr2; @knitr3; @kableextra; @plotly].
```{r eval=FALSE, include=TRUE}
install.packages(c("rmarkdown", "knitr", "kableExtra",
                   "stargazer", "plotly", "knitr",
                   "bookdown"))
```
* ...download the 5 input files I created --- `paper.rmd`, `references.bib`, `data.csv` and `american-sociological-association.csl` --- from [this folder](https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing). Ignore the other files.

@@

* ...a `paper.rmd` file (the underlying R Markdown file).
* ...a `references.bib` file (the bibliography).
    + I use paperpile to manage my references and export the `.bib` file into the folder that contains my `.rmd` file.
* ...a `data.csv` file (some raw data).
* ... a `american-sociological-association.csl` file that defines the style of your bibliography.^[You can download various citation style files from this webpage: https://github.com/citation-style-language/styles.]

@@

```{r tab3, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, results="asis"}
library(knitr)
library(kableExtra)
kable(cars[1:10,], row.names = TRUE, 
      caption = 'Table with kable() and kablestyling()', 
      format = "latex", booktabs = T) %>%
        kable_styling(full_width = T, 
                      latex_options = c("striped", 
                                        "scale_down",
                                        "HOLD_position"),
                      font_size = 10)
```

@@

# Additional tricks for publishing
* Make your script anonymous
    + Simply put a `<!-- ... -->` around any identifying information, e.g., author names, title footnote etc.
* Counting words
    + Use adobe acrobat (commerical software) to convert your file to a word file. Then open in word and delete all the parts that shouldn't go into the word count. The word count is displayed in the lower right.
    + Use an one of the online services to count your words (search for "pdf word count")
* Appendix: You can change the numbering format for the appendix in the rmd file
    + What is still not possible in this document is to automatically have separate reference sections for paper and appendix.
* Journals may require you to use their tex style: Sometimes you can simply use their template in your rmarkdown file. See [here](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/LDUMNY) for a PLOS one example.

### 2020-07-08 paper.tex
Deleted header.tex because of errors.

\usepackage[english]{babel}

@@

\usepackage{graphicx}
\usepackage{url}
\usepackage{graphics}
%\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{natbib}

@@

\usepackage{caption}
\usepackage{subcaption}
\usepackage{fullpage}
\usepackage{multicol}
\usepackage{dcolumn}
\usepackage{lscape}

\usepackage{cleveref}[2012/02/15]
\usepackage{fullpage}
\usepackage[charter]{mathdesign}
\usepackage{bm}
\usepackage{tabu}
\usepackage{wrapfig}

\crefformat{footnote}{#2\footnotemark[#1]#3}
\usepackage{color}
\usepackage{hyperref}

\newenvironment{tightcenter}{%
  \setlength\topsep{0pt}
  \setlength\parskip{0pt}
  \begin{center}
}{%
  \end{center}
}

%\setstretch{1.1}
% Dutch style of paragraph formatting
\parskip 5pt
\makeatletter
% Separation between lines
\doublerulesep 1pt

\definecolor{lightred}{rgb}{0.7,0,0}
\definecolor{darkgreen}{rgb}{0,0.8,0}
\definecolor{lightblue}{rgb}{0,0,0.7}

\hypersetup{colorlinks,
  linkcolor = lightred,
  filecolor = lightred,
  urlcolor = lightblue,
  citecolor = lightred}

% Spaces in bibliography
\let\oldthebibliography=\thebibliography
\let\endoldthebibliography=\endthebibliography
\renewenvironment{thebibliography}[1]{%
  \begin{oldthebibliography}{#1}%
    \setlength{\parskip}{0ex}%
    \setlength{\itemsep}{0.1ex}%
  }%
  {%
  \end{oldthebibliography}%
}

\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\setlength{\parindent}{0pt} % no indentation
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
\date{5 April, 2020\\
~\\
Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

@@

\begin{itemize}
\item
  \ldots download the 5 input files I created --- \texttt{paper.rmd}, \texttt{header.tex}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}. Ignore the other files.
\item
  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \ldots a \texttt{paper.rmd} file (the underlying R Markdown file).
\item
  \ldots a \texttt{header.tex} file (a tex file for document structure).
\item
  \ldots a \texttt{references.bib} file (the bibliography).

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(knitr)}
\KeywordTok{library}\NormalTok{(kableExtra)}
\KeywordTok{kable}\NormalTok{(cars[}\DecValTok{1}\OperatorTok{:}\DecValTok{10}\NormalTok{,], }\DataTypeTok{row.names =} \OtherTok{TRUE}\NormalTok{, }
      \DataTypeTok{caption =} \StringTok{'Table with kable() and kablestyling()'}\NormalTok{, }
      \DataTypeTok{format =} \StringTok{"latex"}\NormalTok{, }\DataTypeTok{booktabs =}\NormalTok{ T) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{kable_styling}\NormalTok{(}\DataTypeTok{full_width =}\NormalTok{ T, }
                      \DataTypeTok{latex_options =} \KeywordTok{c}\NormalTok{(}\StringTok{"striped"}\NormalTok{, }
                                        \StringTok{"scale_down"}\NormalTok{,}
                                        \StringTok{"HOLD_position"}\NormalTok{),}
                      \DataTypeTok{font_size =} \DecValTok{10}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
## R version 3.6.2 (2019-12-12)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 10 x64 (build 17763)
## 
## Matrix products: default
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.2.1    kableExtra_1.1.0 knitr_1.26       stargazer_5.2.2 
## 
## loaded via a namespace (and not attached):
##  [1] Rcpp_1.0.3        pillar_1.4.3      compiler_3.6.2    tools_3.6.2      
##  [5] digest_0.6.23     evaluate_0.14     tibble_2.1.3      lifecycle_0.2.0  
##  [9] gtable_0.3.0      viridisLite_0.3.0 pkgconfig_2.0.3   rlang_0.4.5      
## [13] rstudioapi_0.10   yaml_2.2.0        xfun_0.11         withr_2.1.2      
## [17] dplyr_0.8.3       httr_1.4.1        stringr_1.4.0     xml2_1.2.2       
## [21] vctrs_0.2.4       hms_0.5.2         tidyselect_0.2.5  webshot_0.5.2    
## [25] grid_3.6.2        glue_1.3.2        R6_2.4.1          rmarkdown_2.0    
## [29] bookdown_0.16     farver_2.0.1      purrr_0.3.3       readr_1.3.1      
## [33] magrittr_1.5      scales_1.1.0      htmltools_0.4.0   assertthat_0.2.1 
## [37] rvest_0.3.5       colorspace_1.4-1  labeling_0.3      stringi_1.4.3    
## [41] lazyeval_0.2.2    munsell_0.5.0     crayon_1.3.4
\end{verbatim}

>>>>

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{wrapfig}

@@

\usepackage{colortbl}

@@

\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

\title{\vspace{1cm}Writing a reproducible paper\\
in R Markdown*\footnote{*Corresponding address: \href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}. Acknowledgments: I am grateful to all those generous people that invest their time into open-source software.}\vspace{0.5cm}\\}
\author{Paul C. Bauer\\
Mannheim Centre for European Social Research}
\date{First version: December 14, 2018\\
This version: July 08, 2020\\
~\\
Feedback?\\
\href{mailto:mail@paulcbauer.eu}{\nolinkurl{mail@paulcbauer.eu}}\\}

@@

\begin{itemize}
\item
  \ldots download the 5 input files I created --- \texttt{paper.rmd}, \texttt{references.bib}, \texttt{data.csv} and \texttt{american-sociological-association.csl} --- from \href{https://drive.google.com/drive/folders/1zJP3cNPrHN-gj0rcmbHQgg-XA0hqDXdd?usp=sharing}{this folder}. Ignore the other files.
\item
  \ldots learn R and read about the other underlying components namely \href{https://en.wikipedia.org/wiki/Markdown}{Markdown}, \href{https://rmarkdown.rstudio.com/lesson-1.html}{R Markdown} and \href{https://en.wikipedia.org/wiki/LaTeX}{Latex}.
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \ldots a \texttt{paper.rmd} file (the underlying R Markdown file).
\item
  \ldots a \texttt{references.bib} file (the bibliography).

@@

@@

\begin{verbatim}
## R version 4.0.0 (2020-04-24)
## Platform: x86_64-w64-mingw32/x64 (64-bit)
## Running under: Windows 10 x64 (build 17763)
## 
## Matrix products: default
## 
## attached base packages:
## [1] stats     graphics  grDevices utils     datasets  methods   base     
## 
## other attached packages:
## [1] ggplot2_3.3.0    kableExtra_1.1.0 knitr_1.29       stargazer_5.2.2 
## 
## loaded via a namespace (and not attached):
##  [1] Rcpp_1.0.4.6      pillar_1.4.4      compiler_4.0.0    tools_4.0.0      
##  [5] digest_0.6.25     evaluate_0.14     lifecycle_0.2.0   tibble_3.0.1     
##  [9] gtable_0.3.0      viridisLite_0.3.0 pkgconfig_2.0.3   rlang_0.4.6      
## [13] rstudioapi_0.11   yaml_2.2.1        xfun_0.15         withr_2.2.0      
## [17] stringr_1.4.0     httr_1.4.1        dplyr_1.0.0       xml2_1.3.2       
## [21] generics_0.0.2    vctrs_0.3.1       hms_0.5.3         tidyselect_1.1.0 
## [25] webshot_0.5.2     grid_4.0.0        glue_1.4.1        R6_2.4.1         
## [29] rmarkdown_2.3     bookdown_0.19     farver_2.0.3      purrr_0.3.4      
## [33] readr_1.3.1       magrittr_1.5      scales_1.1.1      ellipsis_0.3.1   
## [37] htmltools_0.5.0   rvest_0.3.5       colorspace_1.4-1  labeling_0.3     
## [41] stringi_1.4.6     munsell_0.5.0     crayon_1.3.4
\end{verbatim}
